Generating the Blueprints of the Java Ecosystem

### 2015-02-27 msr.tex
still working

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{c}
   \affaddr{\aueb Dept of Management Science and Technology}\\
   \affaddr{Athens University of Economics and Business}\\
   \affaddr{Athens, Greece}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
  \end{tabular}
  \centering
  \begin{tabular}{cc}
   \affaddr{} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{g.gousios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{import-process}
\caption{The dataset construction process}
\label{fig:dataset-construction}
\end{figure}

@@

The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl} for the Java ecosystem. The related metrics can be found in the database table named \textit{measuremnt\_type}, these are: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}. With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset. We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects

\begin{table}
\centering
\caption{Popular DSL Usage Combinations}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
XML, XPath, XSLT & 39\\
Regex, XML, XPath, XSLT & 38\\
HTML & 23\\
Regex, XML, XPath & 20\\
Regex, SQL, XML, XPath, XSLT & 18\\
SQL, XML, XPath, XSLT & 11\\
HTML, Regex, XML & 10\\
HTML, XML & 10\\
\hline
\end{tabular}
\end{table}

>>>>

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Georgios Gousios\run \and Diomidis Spinellis\aueb \and Panos Louridas\aueb\\
  \begin{tabular}{c}
   \affaddr{\aueb Dept of Management Science and Technology}\\
   \affaddr{Athens University of Economics and Business}\\
   \affaddr{Athens, Greece}\\
   \email{\{bkarak,dds,louridas\}@aueb.gr}\\
  \end{tabular}
  \centering
  \begin{tabular}{cc}
   \affaddr{} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{g.gousios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{import-process}
\caption{The dataset construction process}
\label{fig:dataset-construction}
\end{figure}

@@

The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl} for the Java ecosystem. The related metrics can be found in the database table named \textit{measuremnt\_type}, these are: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}. With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset. We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects (13\%). Regular expressions are second most popular with 909 occurrences (7\%). Note that these number represents the projects that {\sc xml} and regular expressions were used a sole {\sc dsl}s.

\begin{table}
\centering
\caption{DSL Usage Combinations Ranking}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
XML, XPath, XSLT & 39\\
Regex, XML, XPath, XSLT & 38\\
HTML & 23\\
Regex, XML, XPath & 20\\
Regex, SQL, XML, XPath, XSLT & 18\\
SQL, XML, XPath, XSLT & 11\\
HTML, Regex, XML & 10\\
HTML, XML & 10\\
\hline
\end{tabular}
\end{table}
